Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-05 documentation/paper.tex
Removed unnecessary hardware section

\section{Technologies}

\subsection{Software}

All programming for this study was done in Python 3. Keras \cite{keras} was used for all machine learning tasks. NumPy and SciPy were used for linear algebra and signal processing. ROOT, scikit-image and scikit-learn were used for data loading and storage. Matplotlib was used for data visualization.

\subsection{Hardware}

Training was done on the Graham supercomputer at the University of Waterloo, accessed through Compute Canada and SHARCNET. I would like to thank Ken Clark and SNOLAB very much for generously providing access to this hardware.

>>>>

\section{Software}

All programming for this study was done in Python 3. Keras \cite{keras}, running on a TensorFlow backend, was used for all machine learning tasks. NumPy and SciPy were used for linear algebra and signal processing. ROOT, scikit-image and scikit-learn were used for data loading and storage. Matplotlib was used for data visualization.
